---
format: dashboard
---

#  {.tabset .tabset-pills}

## Daily programme {.tabset}

### Monday

**Epiverse-TRACE Perspectives**

Day 1 will be focused on the presentation of the project perspectives, particularly the planning for its second phase. Attendees will have the opportunity to discuss and review the draft planning document prepared by the PIs.

**Venue**: [Sir Dawda Kairaba Jawara International Conference Center](https://www.oicgambia.org/sdkj-icc), Serrekunda.

**Objectives**:

-   Opening of the summit.
-   Discuss the implementation of Phase 2 of the Epiverse-TRACE project.

**Expected Outcomes**:

-   Gather reviews and feedback to strengthen the proposal for the phase 2 roadmap.

**Moderators**:

Bubacarr & Uyi

```{r eval=TRUE, echo = FALSE}
#| classes: plain
day_1_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:00",  "12:00-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Welcome and Registration", "Opening Ceremony and Launching of Phase 2 (Epiverse-TRACE project)", "Coffee Break", "Ice Breaker", "Data.org related activities", "Lunch", "RF & RSE Sessions", "Dinner"),
  Speakers = c("-", "Dr Bubacarr Bah, Prof Umberto D'Alessandro, uyi stewart & MoH representative ", "", "Banky", "Uyi", "", "Degoot & James", "")
)

day_1_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_styling("striped", full_width = TRUE, font_size = 18) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Tuesday

**Inclusivity and Sustainability of Epiverse-TRACE Tools**

Day 2 aims at evaluating phase 1 of the project and discussing the inclusivity and sustainability of the project tools.

**Venue**: Bray conference room, MRCG

**Objectives:**

-   Assess how well the project tools currently address diverse populations and settings.
-   Identify gaps in inclusivity (e.g. language barriers, accessibility).
-   Identify opportunities for collaboration from the gaps and needs from phase 1.
-   Expand the scope of our tools to cover public health threats in other parts of the world.
-   Explore the sustainability of the project.

**Expected Outcomes:**

-   Identification of:
    -   our strengths and weaknesses.
    -   potential collaborators to fulfill the gaps and needs.
    -   ways of covering more health issues.
-   A strategic roadmap for ensuring the continued relevance and use of our tools post-project.

**Moderators:**

Seb, Natalia & Diana

```{r eval=TRUE, echo = FALSE}
#| classes: plain
day_2_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Lessons Learnt and Gaps", "Sustainability of Epidemics Analytic Tools", "Coffee Break", "Inclusivity within Epiverse-TRACE Tools", "Lunch", "RF & RSE Sessions", "Dinner"),
  Speakers = c("Groups Discussion", "Groups Discussion", "", "Expert Presentation", "", "Degoot & James", "")
)
day_2_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 5, 7), color = 'white', background = 'black')
```

### Wednesday

**Site Visits**

-   Kayaking through the River Gambia to Tanji Bird Reserve

-   Visit to the Snake Farm in Kartong

-   Boat Riding to the Confluence of the River and the Ocean

**Note:**

Participation in any of these activities is optional.

**Organizers:**

-   Gibril Gabbidon & Alimatou Sallah

#### Column

![](./images/boat_ride.avif){fig-align="center" width="100%" height="110%"}

### Thursday

**Adoption of Epiverse-TRACE for Small-Scale Outbreaks, NTDs, One Health, and Disease Surveillance**

The sessions on this day will be focused on how the Epiverse-TRACE analytics tools can be applied beyond infectious diseases. Discussions will cover their usage in the context of small-scale local outbreaks, neglected tropical diseases (NTDs), one health perspectives, and in disease surveillance.

**Venue**: Bray conference room, MRCG

**Objectives**:

-   Explore how Epiverse-TRACE tools can be adapted for small-scale local outbreaks and neglected tropical diseases.
-   One Health Approach: Highlight the integration to the one health perspective, considering the interconnection between people, animals, plants, and their shared environment.
-   Enhance Surveillance: Discuss the potential of these tools in enhancing surveillance systems across various health domains.

**Expected Outcomes**:

-   Gain insights into the broader applicability of Epiverse-TRACE tools beyond traditional infectious disease analytics.
-   Identify opportunities for interdisciplinary collaborations and partnerships to enhance surveillance and outbreak response.

**Moderators**:

Zulma, Adam & Nuredin

```{r eval=TRUE, echo = FALSE}
#| classes: plain
day_5_agenda <- data.frame(
  Time = c("09:00-10:00", "10:00-11:00", "11:00-11:30", "11:30-12:30", "12:30-13:00", "13:00-15:00", "15:00-17:00", "19:00-21:00"),
  Activity = c("Local Outbreaks", "NTDs", "Coffee Break", "One Health", "Disease Surveillance",  "Lunch Break", "RF/RSE Sessions", "Dinner"),
  Speakers = c(" Groups Discussion", "Groups Discussion", "", "Groups Discussion", "Groups Discussion", "", "Degoot & James", "")
)

day_5_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 6, 8), color = 'white', background = 'black')
```

### Friday

**Outbreak Analytics Course**

On this last day, participants will bring in their thoughts on how to design a data-centered outbreak analytics course aimed at training and teaching outbreak analysis. It will also reflect on the lessons learnt from previous trainings and identify current gaps within the project and explore ways to overcome them.

**Venue**: Bray conference room & F1 Seminar room, MRCG

**Objectives**:

-   Develop a comprehensive and practical outbreak analytics course that effectively teaches key concepts and methods
-   Identify and discuss existing gaps within the project related to training, tools, and resources.

**Expected Outcomes**:

-   Draft course framework: A preliminary framework for the outbreak analytics course, including key topics, teaching methods, and assessment strategies.
-   Plans to address the gaps, with specific implementation steps.

**Moderators**:

Andree, Degoot & Laura

```{r eval=TRUE, echo = FALSE}
#| classes: plain
day_4_agenda <- data.frame(
  Time = c("09:00-11:00", "11:00-11:30", "11:30-12:00", "12:00-13:00", "13:00-15:00", "19:00-21:00"),
  Activity = c("Designing Outbreak Analytics Course", "Coffee Break", "Closing Remarks", "Unit Seminar", "Lunch", "Dinner"),
  Speakers = c("Groups Discussion", "", "Bubacarr Bah", "Presentation by Adam/Zulma", "", "")
)

day_4_agenda |>
  kableExtra::kbl() |>
  kableExtra::kable_paper("striped", font_size = 18, full_width = TRUE) |>
  kableExtra::row_spec(c(3, 5, 6), color = 'white', background = 'black')
```
